target_offtarget

### 2025-03-29 manuscript_figures.Rmd
Changing virus load axis label to genome copies

ggplot() +
  geom_point(data = depths_reads_sub,
             mapping = aes(Viral.load, mean_depth, color = virus)) +
  geom_abline(data = lm_combined, aes(intercept = `(Intercept)`, slope = log_viral_load), linetype="dotted") +
  geom_text(data = lm_combined,
            colour = "black",
            aes(
              x = 6*10000,
              y = 2,
              label = round(Coeff_x1, digits = 2)),
            size = 3.5) +
  geom_text(data = lm_combined,
            colour = "black",
            aes(x = 1.5*10000, 
                y = 2, 
                label = "Slope ="),
            size = 3.5) +
  geom_text(data = lm_combined,
            colour = "black",
            aes(
              x = 6*10000,
              y = 6,
              label = round(R2, digits = 2)),
            size = 3.5) +
  geom_text(data = lm_combined,
            colour = "black",
            aes(x = 2*10000, 
                y = 6, 
                label = "R2 ="),
            size = 3.5) +
  facet_wrap( ~ virus, labeller = as_labeller(facet_names)) +
  theme_few() +
  theme(
    axis.title.x = element_text(size = 10),
    panel.grid.major = element_line(linewidth=0.1, color = "gray60"),
    panel.grid.minor = element_line(linewidth=0.1, color = "lightgray"),
    axis.title.y = element_text(size = 10),
    legend.title = element_blank()
  ) +
    xlab("Viral load (gc/ml)") + 
  ylab("Mean Read Depth") +
  scale_color_manual(values = cols) +
  guides(color = FALSE) +
  scale_x_log10(labels = scales::trans_format("log10", scales::label_math())) + 
    scale_y_log10(labels = scales::trans_format("log10", scales::label_math()))

@@

## >>>> now redundant? - Figure 1: plots of TE experiment data - read counts and read depths

### Read-in data
```{r}
#ATCC genomes updated version
#October 2024

@@

read_count <- 
  counts_reads_norm |>
  filter(Background != "p6") |>
  filter(Background != "control") |>
  ggplot(aes(
    x = Viral.load,
    y = log10(matched),
    colour = virus
  )) +
  geom_point() +
  geom_smooth(aes(group = virus, linetype = genome_structure), se = FALSE) +
  facet_grid( ~ type, labeller = as_labeller(facet_names)) +
  theme_few() +
  theme(
    axis.title.x = element_text(size = 12),
    axis.text.x = element_text(angle = 0, hjust = 1),
    axis.title.y = element_text(size = 12),
    legend.title = element_blank(),
    legend.position = "top", 
    panel.grid.major = element_line(linewidth=0.1, color = "gray60"),
    panel.grid.minor = element_line(linewidth=0.1, color = "lightgray")
  ) +
  scale_color_manual(
    values = cols,
    labels = c(
      "Human adenovirus 40",
      "Human betaherpesvirus",
      "Human respiratory syncytial virus",
      "Influenza B virus",
      "Mammalian orthoreovirus 3",
      "Zika virus"
    )
  ) +
  ylab("log10(Viral Reads)") +
  xlab("Log (Viral load)") + 
  scale_x_log10(labels = scales::trans_format("log10", scales::label_math()))

#ggsave("figures/compare_spike_ins_atcc/read_counts.pdf",width=8,height=6)

#normalise by raw read count

read_count_norm1 <- counts_reads_norm |>
  filter(Background != "p6") |>
  filter(Background != "control") |>
  ggplot(aes(
    x = Viral.load,
    y = log10(norm_counts1),
    colour = virus
  )) +
  geom_point() +
  geom_smooth(aes(group = virus, linetype = genome_structure), se = FALSE) +
  facet_grid( ~ type, labeller = as_labeller(facet_names)) +
  theme_few() +
  theme(
    axis.title.x = element_text(size = 12),
    axis.text.x = element_text(angle = 0, hjust = 1),
    axis.title.y = element_text(size = 12),
    legend.title = element_blank(),
    legend.position = "top", 
    panel.grid.major = element_line(linewidth=0.1, color = "gray60"),
    panel.grid.minor = element_line(linewidth=0.1, color = "lightgray")
  ) +
  scale_color_manual(
    values = cols,
    labels = c(
      "Human adenovirus 40",
      "Human betaherpesvirus",
      "Human respiratory syncytial virus",
      "Influenza B virus",
      "Mammalian orthoreovirus 3",
      "Zika virus"
    )
  ) +
  ylab("log10(viral reads/cleaned reads)") +
  xlab("Log (Viral load)") + 
  scale_x_log10(labels = scales::trans_format("log10", scales::label_math()))

read_count_norm2 <- 
  counts_reads_norm |>
  filter(Background != "p6") |>
  filter(Background != "control") |>
  ggplot(aes(
    x = (Viral.load),
    y = log10(norm_counts2),
    colour = virus
  )) +
  geom_point() +
  geom_smooth(aes(group = virus, linetype = genome_structure), se = FALSE) +
  facet_grid( ~ type, labeller = as_labeller(facet_names)) +
  theme_few() +
  theme(
    axis.title.x = element_text(size = 12),
    axis.text.x = element_text(angle = 0, hjust = 1),
    axis.title.y = element_text(size = 12),
    legend.title = element_blank(),
    legend.position = "top", 
    panel.grid.major = element_line(linewidth=0.1, color = "gray60"),
    panel.grid.minor = element_line(linewidth=0.1, color = "lightgray")
  ) +
  scale_color_manual(
    values = cols,
    labels = c(
      "Human adenovirus 40",
      "Human betaherpesvirus",
      "Human respiratory syncytial virus",
      "Influenza B virus",
      "Mammalian orthoreovirus 3",
      "Zika virus"
    )
  ) +
  ylab("Log (viral reads/cleaned reads/genome length)") +
  xlab("Log (Viral load)") + 
  scale_x_log10(labels = scales::trans_format("log10", scales::label_math()))

### plot just the two lefthand panels from the original figure
```{r, warning=FALSE, echo=FALSE, message=FALSE, fig.height=10, fig.width=8}

ggarrange(read_count,
          read_count_norm2,
          nrow = 2,
          common.legend = TRUE)

#ggsave("figures/compare_spike_ins_atcc/log_read_count_depth_2panels.png",width=10,height=7)

### plot viral read counts (non normalised)
```{r}

##deduplicated only

read_count_dedup <- 
  counts_reads_norm |>
  filter(Background != "p6") |>
  filter(Background != "control") |>
  filter(type == "dedup_TE") |>
  ggplot(aes(
    x = Viral.load,
    y = log10(matched),
    colour = virus
  )) +
  geom_point() +
  geom_smooth(aes(group = virus, linetype = genome_structure), se = FALSE, method = "lm") +
  theme_few() +
  theme(
    axis.title.x = element_text(size = 12),
    axis.text.x = element_text(angle = 0, hjust = 1),
    axis.title.y = element_text(size = 12),
    legend.title = element_blank(),
    legend.position = "top", 
    panel.grid.major = element_line(linewidth=0.1, color = "gray60"),
    panel.grid.minor = element_line(linewidth=0.1, color = "lightgray")
  ) +
  scale_color_manual(
    values = cols,
    labels = c(
      "Human adenovirus 40",
      "Human betaherpesvirus",
      "Human respiratory syncytial virus",
      "Influenza B virus",
      "Mammalian orthoreovirus 3",
      "Zika virus"
    )
  ) +
  ylab("Log (Viral Reads)") +
  xlab("Log (Viral load)") + 
  scale_x_log10(labels = scales::trans_format("log10", scales::label_math()))

read_count_norm2_dedup <- 
  counts_reads_norm |>
  filter(Background != "p6") |>
  filter(Background != "control") |>
  filter(type == "dedup_TE") |>
  ggplot(aes(
    x = Viral.load,
    y = log10(norm_counts2),
    colour = virus
  )) +
  geom_point() +
  geom_smooth(aes(group = virus, linetype = genome_structure), se = FALSE, method = "lm") +
  theme_few() +
  theme(
    axis.title.x = element_text(size = 12),
    axis.text.x = element_text(angle = 0, hjust = 1),
    axis.title.y = element_text(size = 12),
    legend.title = element_blank(),
    legend.position = "top", 
    panel.grid.major = element_line(linewidth=0.1, color = "gray60"),
    panel.grid.minor = element_line(linewidth=0.1, color = "lightgray")
  ) +
  scale_color_manual(
    values = cols,
    labels = c(
      "Human adenovirus 40",
      "Human betaherpesvirus",
      "Human respiratory syncytial virus",
      "Influenza B virus",
      "Mammalian orthoreovirus 3",
      "Zika virus"
    )
  ) +
  ylab("Log (viral reads/cleaned reads/genome length)") +
  xlab("Log (Viral load)") + 
  scale_x_log10(labels = scales::trans_format("log10", scales::label_math()))
```

### ***Final plot***
```{r, warning=FALSE, message=FALSE, echo=FALSE, fig.width=8, fig.height=10}
#plot just the two lefthand panels from the original figure

ggarrange(
  read_count_dedup,
  read_count_norm2_dedup,
  nrow = 2,
  common.legend = TRUE,
  align = "hv"
)

# ggsave("figures/compare_spike_ins_atcc/log_read_count_depth_2panels_dedup.png",
#        width=10,
#        height=7)

ggsave("figures/manuscript_figure_2025/PDF/Figure_S1.pdf",
       width=7,
       height=8)

ggsave("figures/manuscript_figure_2025/PNG/Figure_S1.png",
       width=7,
       height=8)

@@

read_depths <- 
  depths_reads |>
  filter(Background != "p6") |>
  filter(Background != "control") |>
  ggplot(aes(
    x = Viral.load,
    y = log10(mean_depth),
    colour = virus
  )) +
  geom_point() +
  geom_smooth(aes(group = virus, linetype = genome_structure), se = FALSE) +
  facet_grid( ~ type, labeller = as_labeller(facet_names)) +
  theme_few() +
  theme(
    axis.title.x = element_text(size = 12),
    axis.text.x = element_text(angle = 0, hjust = 1),
    axis.title.y = element_text(size = 12),
    legend.title = element_blank(),
    legend.position = "top", 
    panel.grid.major = element_line(linewidth=0.1, color = "gray60"),
    panel.grid.minor = element_line(linewidth=0.1, color = "lightgray")
  ) +
  scale_color_manual(
    values = cols,
    labels = c(
      "Human adenovirus 40",
      "Human betaherpesvirus",
      "Human respiratory syncytial virus",
      "Influenza B virus",
      "Mammalian orthoreovirus 3",
      "Zika virus"
    )
  ) +
  ylab("Log (mean read depth)") +
  xlab("Log (Viral load)") + 
  scale_x_log10(labels = scales::trans_format("log10", scales::label_math()))

@@

pool_counts_sum <- 
  counts_pool |>
  filter(Background != "p6") |>
  filter(Background != "control") |>
  ggplot(aes(
    x = as.character(Viral.load),
    y = log10(matched),
    colour = Pool
  )) +
  geom_boxplot() +
  facet_grid( ~ type, labeller = as_labeller(facet_names)) +
  theme_few() +
  theme(
    axis.title.x = element_blank(),
    # axis.text.x = element_blank(),
    legend.title = element_blank(),
    axis.title.y = element_text(size = 10),
    panel.grid.major = element_line(linewidth=0.1, color = "gray60"),
    panel.grid.minor = element_line(linewidth=0.1, color = "lightgray")
  ) +
  ylab("Log (Viral Reads)") + xlab("Log (Viral load)") +
  scale_color_manual(values = cols3, labels = c("Pool 1", "Pool 2")) + 
  scale_x_discrete(labels = c(bquote(10^{2}), bquote(10^{3}), bquote(10^{5})))

@@

pool_norm1_sum <- 
  counts_pool |>
  filter(Background != "p6") |>
  filter(Background != "control") |>
  ggplot(aes(
    x = as.character(Viral.load),
    y = log10(matched),
    colour = Pool
  )) +
  geom_boxplot() +
  facet_grid( ~ type, labeller = as_labeller(facet_names)) +
  theme_few() +
  theme(
    axis.title.x = element_blank(),
    # axis.text.x = element_blank(),
    legend.title = element_blank(),
    axis.title.y = element_text(size = 10),
    panel.grid.major = element_line(linewidth=0.1, color = "gray60"),
    panel.grid.minor = element_line(linewidth=0.1, color = "lightgray") 
  ) +
  ylab("log10(viral reads/cleaned reads)") + xlab("Log (Viral load)") +
  scale_color_manual(values = cols3, labels = c("Pool 1", "Pool 2")) + 
    scale_x_discrete(labels = c(bquote(10^{2}), bquote(10^{3}), bquote(10^{5})))

@@

pool_norm2_sum <- 
  counts_pool |>
  filter(Background != "p6") |>
  filter(Background != "control") |>
  ggplot(aes(
    x = as.character(Viral.load),
    y = log10(matched),
    colour = Pool
  )) +
  geom_boxplot() +
  facet_grid( ~ type, labeller = as_labeller(facet_names)) +
  theme_few() +
  theme(
    axis.title.x = element_blank(),
    # axis.text.x = element_blank(),
    legend.title = element_blank(),
    axis.title.y = element_text(size = 10),
    panel.grid.major = element_line(linewidth=0.1, color = "gray60"),
    panel.grid.minor = element_line(linewidth=0.1, color = "lightgray")
  ) +
  ylab("log10(viral reads/cleaned reads/genome length)") + xlab("Log (Viral load)") +
  scale_color_manual(values = cols3, labels = c("Pool 1", "Pool 2")) + 
    scale_x_discrete(labels = c(bquote(10^{2}), bquote(10^{3}), bquote(10^{5})))

@@

pool_depths_sum <-
  depths_pool |>
  filter(Background != "p6") |>
  filter(Background != "control") |>
  ggplot(aes(
    x = as.character(Viral.load),
    y = log10(mean_depth),
    colour = Pool
  )) +
  geom_boxplot() +
  facet_grid( ~ type, labeller = as_labeller(facet_names)) +
  theme_few() +
  theme(
    axis.title.x = element_blank(),
    # axis.text.x = element_blank(),
    legend.title = element_blank(),
    axis.title.y = element_text(size = 10),
    panel.grid.major = element_line(linewidth=0.1, color = "gray60"),
    panel.grid.minor = element_line(linewidth=0.1, color = "lightgray")
  ) +
  ylab("Log (mean read depth)") +
  xlab("Log (Viral load)") + 
  scale_x_discrete(labels = c(bquote(10^{2}), bquote(10^{3}), bquote(10^{5}))) +
  scale_color_manual(values = cols3, labels = c("Pool 1", "Pool 2"))

@@

ggsave("figures/manuscript_figure_2025/PDF/Figure_S2.pdf",
       width = 10,
       height = 7)

ggsave("figures/manuscript_figure_2025/PNG/Figure_S2.png",
       width = 10,
       height = 7)

@@

total_reads <- 
  reads_plot |>
  filter(Background != "p6") |>
  filter(Background != "control") |>
  ggplot(aes(
    x = Viral.load,
    y = (total_reads),
    colour = Background
  )) +
  geom_point() +
  geom_smooth(aes(group = Background), se = FALSE) +
  facet_grid( ~ type, labeller = as_labeller(facet_names)) +
  theme_few() +
  theme(
    axis.title.y = element_text(size = 10),
    panel.grid.major = element_line(linewidth=0.1, color = "gray60"),
    panel.grid.minor = element_line(linewidth=0.1, color = "lightgray")
  ) +
  scale_y_log10(labels = scales::trans_format("log10", scales::label_math())) + 
    scale_x_log10(labels = scales::trans_format("log10", scales::label_math())) + xlab("Viral load") +
  # ggtitle("All") +
  ylab("Total number of reads") +
  scale_color_manual(values = cols2, labels = c("P1", "P2"))

viral_reads <- 
  reads_plot |>
  filter(Background != "p6") |>
  filter(Background != "control") |>
  ggplot(aes(
    x = Viral.load,
    y = (viral_reads),
    colour = Background
  )) +
  geom_point() +
  geom_smooth(aes(group = Background), se = FALSE) +
  facet_grid( ~ type, labeller = as_labeller(facet_names)) +
  theme_few() +
  theme(
    axis.title.y = element_text(size = 10),
    panel.grid.major = element_line(linewidth=0.1, color = "gray60"),
    panel.grid.minor = element_line(linewidth=0.1, color = "lightgray")
  ) +
  scale_y_log10(labels = scales::trans_format("log10", scales::label_math())) + 
    scale_x_log10(labels = scales::trans_format("log10", scales::label_math())) + xlab("Viral load") +
  # ggtitle("Viral reads") +
  ylab("Number of viral reads") +
  scale_color_manual(values = cols2, labels = c("P1", "P2"))

ATCC_reads <- 
  reads_plot |>
  filter(Background != "p6") |>
  filter(Background != "control") |>
  ggplot(aes(
    x = Viral.load,
    y = (ATCC_reads),
    colour = Background
  )) +
  geom_point() +
  geom_smooth(aes(group = Background), se = FALSE) +
  facet_grid( ~ type, labeller = as_labeller(facet_names)) +
  theme_few() +
  theme(
    axis.title.y = element_text(size = 10),
    panel.grid.major = element_line(linewidth=0.1, color = "gray60"),
    panel.grid.minor = element_line(linewidth=0.1, color = "lightgray")
  ) +
  scale_y_log10(labels = scales::trans_format("log10", scales::label_math())) + 
    scale_x_log10(labels = scales::trans_format("log10", scales::label_math())) + xlab("Viral load") +
  ggtitle("Spike-in Viral Reads") +
  ylab("Spike-in Viral Reads") +
  scale_color_manual(values = cols2, labels = c("P1", "P2"))

prop_ATCC <- reads_plot |>
  filter(Background != "p6") |>
  filter(Background != "control") |>
  ggplot(aes(x = Viral.load, y = prop_ATCC, colour = Background)) +
  geom_point() +
  geom_smooth(aes(group = Background), se = FALSE) +
  facet_grid( ~ type, labeller = as_labeller(facet_names)) +
  theme_few() +
  theme(
    axis.title.y = element_text(size = 10),
    panel.grid.major = element_line(linewidth=0.1, color = "gray60"),
    panel.grid.minor = element_line(linewidth=0.1, color = "lightgray")
  ) +
    scale_x_log10(labels = scales::trans_format("log10", scales::label_math())) + xlab("Viral load") +
  ggtitle("Spike-in viral reads") +
  ylab("Proportion") +
  scale_color_manual(values = cols2, labels = c("P1", "P2"))

prop_viral <- reads_plot |>
  filter(Background != "p6") |>
  filter(Background != "control") |>
  ggplot(aes(x = Viral.load, y = prop_viral, colour = Background)) +
  geom_point() +
  geom_smooth(aes(group = Background), se = FALSE) +
  facet_grid( ~ type, labeller = as_labeller(facet_names)) +
  theme_few() +
  theme(
    axis.title.y = element_text(size = 10),
    panel.grid.major = element_line(linewidth=0.1, color = "gray60"),
    panel.grid.minor = element_line(linewidth=0.1, color = "lightgray")
  ) +
 scale_x_log10(labels = scales::trans_format("log10", scales::label_math())) + xlab("Viral load") +
  # ggtitle("Viral reads") +
  ylab("Proportion of viral reads") +
  scale_color_manual(values = cols2, labels = c("P1", "P2")) + scale_y_continuous(limits=c(0,1.0))

>>>>

ggplot() +
  geom_point(data = depths_reads_sub,
             mapping = aes(Viral.load, mean_depth, color = virus)) +
  geom_abline(data = lm_combined, aes(intercept = `(Intercept)`, slope = log_viral_load), linetype="dotted") +
  geom_text(data = lm_combined,
            colour = "black",
            aes(
              x = 6*10000,
              y = 2,
              label = round(Coeff_x1, digits = 2)),
            size = 3.5) +
  geom_text(data = lm_combined,
            colour = "black",
            aes(x = 1.5*10000, 
                y = 2, 
                label = "Slope ="),
            size = 3.5) +
  geom_text(data = lm_combined,
            colour = "black",
            aes(
              x = 6*10000,
              y = 6,
              label = round(R2, digits = 2)),
            size = 3.5) +
  geom_text(data = lm_combined,
            colour = "black",
            aes(x = 2*10000, 
                y = 6, 
                label = "R2 ="),
            size = 3.5) +
  facet_wrap( ~ virus, labeller = as_labeller(facet_names)) +
  theme_few() +
  theme(
    axis.title.x = element_text(size = 10),
    panel.grid.major = element_line(linewidth=0.1, color = "gray60"),
    panel.grid.minor = element_line(linewidth=0.1, color = "lightgray"),
    axis.title.y = element_text(size = 10),
    legend.title = element_blank()
  ) +
    xlab("Genome copies") + 
  ylab("Mean Read Depth") +
  scale_color_manual(values = cols) +
  guides(color = FALSE) +
  scale_x_log10(labels = scales::trans_format("log10", scales::label_math())) + 
    scale_y_log10(labels = scales::trans_format("log10", scales::label_math()))

@@

### Read counts
```{r}
### Read-in data

#ATCC genomes updated version
#October 2024

@@

@@

read_count <- 
  counts_reads_norm |>
  filter(Background != "p6") |>
  filter(Background != "control") |>
  ggplot(aes(
    x = Viral.load,
    y = log10(matched),
    colour = virus
  )) +
  geom_point() +
  geom_smooth(aes(group = virus, linetype = genome_structure), se = FALSE) +
  facet_grid( ~ type, labeller = as_labeller(facet_names)) +
  theme_few() +
  theme(
    axis.title.x = element_text(size = 12),
    axis.text.x = element_text(angle = 0, hjust = 1),
    axis.title.y = element_text(size = 12),
    legend.title = element_blank(),
    legend.position = "top", 
    panel.grid.major = element_line(linewidth=0.1, color = "gray60"),
    panel.grid.minor = element_line(linewidth=0.1, color = "lightgray")
  ) +
  scale_color_manual(
    values = cols,
    labels = c(
      "Human adenovirus 40",
      "Human betaherpesvirus",
      "Human respiratory syncytial virus",
      "Influenza B virus",
      "Mammalian orthoreovirus 3",
      "Zika virus"
    )
  ) +
  scale_linetype_manual(values=c(2, 1)) +
  ylab("log10(Viral Reads)") +
  xlab("Genome copies") + 
  scale_x_log10(labels = scales::trans_format("log10", scales::label_math()))

read_count_norm1 <- 
  counts_reads_norm |>
  filter(Background != "p6") |>
  filter(Background != "control") |>
  ggplot(aes(
    x = Viral.load,
    y = log10(norm_counts1),
    colour = virus
  )) +
  geom_point() +
  geom_smooth(aes(group = virus, linetype = genome_structure), se = FALSE) +
  facet_grid( ~ type, labeller = as_labeller(facet_names)) +
  theme_few() +
  theme(
    axis.title.x = element_text(size = 12),
    axis.text.x = element_text(angle = 0, hjust = 1),
    axis.title.y = element_text(size = 12),
    legend.title = element_blank(),
    legend.position = "top", 
    panel.grid.major = element_line(linewidth=0.1, color = "gray60"),
    panel.grid.minor = element_line(linewidth=0.1, color = "lightgray")
  ) +
  scale_color_manual(
    values = cols,
    labels = c(
      "Human adenovirus 40",
      "Human betaherpesvirus",
      "Human respiratory syncytial virus",
      "Influenza B virus",
      "Mammalian orthoreovirus 3",
      "Zika virus"
    )
  ) +
  scale_linetype_manual(values=c(2, 1)) +
  ylab("log10(viral reads/cleaned reads)") +
  xlab("Genome copies") + 
  scale_x_log10(labels = scales::trans_format("log10", scales::label_math()))

read_count_norm2 <- 
  counts_reads_norm |>
  filter(Background != "p6") |>
  filter(Background != "control") |>
  ggplot(aes(
    x = (Viral.load),
    y = log10(norm_counts2),
    colour = virus
  )) +
  geom_point() +
  geom_smooth(aes(group = virus, linetype = genome_structure), se = FALSE) +
  facet_grid( ~ type, labeller = as_labeller(facet_names)) +
  theme_few() +
  theme(
    axis.title.x = element_text(size = 12),
    axis.text.x = element_text(angle = 0, hjust = 1),
    axis.title.y = element_text(size = 12),
    legend.title = element_blank(),
    legend.position = "top", 
    panel.grid.major = element_line(linewidth=0.1, color = "gray60"),
    panel.grid.minor = element_line(linewidth=0.1, color = "lightgray")
  ) +
  scale_color_manual(
    values = cols,
    labels = c(
      "Human adenovirus 40",
      "Human betaherpesvirus",
      "Human respiratory syncytial virus",
      "Influenza B virus",
      "Mammalian orthoreovirus 3",
      "Zika virus"
    )
  ) +
  scale_linetype_manual(values=c(2, 1)) +
  ylab("Log (viral reads/cleaned reads/genome length)") +
  xlab("Genome copies") + 
  scale_x_log10(labels = scales::trans_format("log10", scales::label_math()))

read_depths <- 
  depths_reads |>
  filter(Background != "p6") |>
  filter(Background != "control") |>
  ggplot(aes(
    x = Viral.load,
    y = log10(mean_depth),
    colour = virus
  )) +
  geom_point() +
  geom_smooth(aes(group = virus, linetype = genome_structure), se = FALSE) +
  facet_grid( ~ type, labeller = as_labeller(facet_names)) +
  theme_few() +
  theme(
    axis.title.x = element_text(size = 12),
    axis.text.x = element_text(angle = 0, hjust = 1),
    axis.title.y = element_text(size = 12),
    legend.title = element_blank(),
    legend.position = "top", 
    panel.grid.major = element_line(linewidth=0.1, color = "gray60"),
    panel.grid.minor = element_line(linewidth=0.1, color = "lightgray")
  ) +
  scale_color_manual(
    values = cols,
    labels = c(
      "Human adenovirus 40",
      "Human betaherpesvirus",
      "Human respiratory syncytial virus",
      "Influenza B virus",
      "Mammalian orthoreovirus 3",
      "Zika virus"
    )
  ) +
  scale_linetype_manual(values=c(2, 1)) +
  ylab("Log (mean read depth)") +
  xlab("Genome copies") + 
  scale_x_log10(labels = scales::trans_format("log10", scales::label_math()))

@@

pool_counts_sum <- 
  counts_pool |>
  filter(Background != "p6") |>
  filter(Background != "control") |>
  ggplot(aes(
    x = as.character(Viral.load),
    y = log10(matched),
    colour = Pool
  )) +
  geom_boxplot() +
  facet_grid( ~ type, labeller = as_labeller(facet_names)) +
  theme_few() +
  theme(
    # axis.title.x = element_blank(),
    # axis.text.x = element_blank(),
    legend.title = element_blank(),
    axis.title.y = element_text(size = 10),
    panel.grid.major = element_line(linewidth=0.1, color = "gray60"),
    panel.grid.minor = element_line(linewidth=0.1, color = "lightgray")
  ) +
  ylab("Log (Viral Reads)") + xlab("Genome copies") +
  scale_color_manual(values = cols3, labels = c("Pool 1", "Pool 2")) + 
  scale_x_discrete(labels = c(bquote(10^{2}), bquote(10^{3}), bquote(10^{5})))

@@

pool_norm1_sum <- 
  counts_pool |>
  filter(Background != "p6") |>
  filter(Background != "control") |>
  ggplot(aes(
    x = as.character(Viral.load),
    y = log10(matched),
    colour = Pool
  )) +
  geom_boxplot() +
  facet_grid( ~ type, labeller = as_labeller(facet_names)) +
  theme_few() +
  theme(
    # axis.title.x = element_blank(),
    # axis.text.x = element_blank(),
    legend.title = element_blank(),
    axis.title.y = element_text(size = 10),
    panel.grid.major = element_line(linewidth=0.1, color = "gray60"),
    panel.grid.minor = element_line(linewidth=0.1, color = "lightgray") 
  ) +
  ylab("Log (viral reads/cleaned reads)") + xlab("Genome copies") +
  scale_color_manual(values = cols3, labels = c("Pool 1", "Pool 2")) + 
    scale_x_discrete(labels = c(bquote(10^{2}), bquote(10^{3}), bquote(10^{5})))

@@

pool_norm2_sum <- 
  counts_pool |>
  filter(Background != "p6") |>
  filter(Background != "control") |>
  ggplot(aes(
    x = as.character(Viral.load),
    y = log10(matched),
    colour = Pool
  )) +
  geom_boxplot() +
  facet_grid( ~ type, labeller = as_labeller(facet_names)) +
  theme_few() +
  theme(
    # axis.title.x = element_blank(),
    # axis.text.x = element_blank(),
    legend.title = element_blank(),
    axis.title.y = element_text(size = 10),
    panel.grid.major = element_line(linewidth=0.1, color = "gray60"),
    panel.grid.minor = element_line(linewidth=0.1, color = "lightgray")
  ) +
  ylab("Log (viral reads/cleaned reads/genome length)") + xlab("Genome copies") +
  scale_color_manual(values = cols3, labels = c("Pool 1", "Pool 2")) + 
    scale_x_discrete(labels = c(bquote(10^{2}), bquote(10^{3}), bquote(10^{5})))

@@

pool_depths_sum <-
  depths_pool |>
  filter(Background != "p6") |>
  filter(Background != "control") |>
  ggplot(aes(
    x = as.character(Viral.load),
    y = log10(mean_depth),
    colour = Pool
  )) +
  geom_boxplot() +
  facet_grid( ~ type, labeller = as_labeller(facet_names)) +
  theme_few() +
  theme(
    # axis.title.x = element_blank(),
    # axis.text.x = element_blank(),
    legend.title = element_blank(),
    axis.title.y = element_text(size = 10),
    panel.grid.major = element_line(linewidth=0.1, color = "gray60"),
    panel.grid.minor = element_line(linewidth=0.1, color = "lightgray")
  ) +
  ylab("Log (mean read depth)") +
  xlab("Genome copies") + 
  scale_x_discrete(labels = c(bquote(10^{2}), bquote(10^{3}), bquote(10^{5}))) +
  scale_color_manual(values = cols3, labels = c("Pool 1", "Pool 2"))

@@

ggsave("figures/manuscript_figure_2025/PDF/Figure_S2.pdf",
       width = 12,
       height = 8)

ggsave("figures/manuscript_figure_2025/PNG/Figure_S2.png",
       width = 12,
       height = 8)

@@

total_reads <- 
  reads_plot |>
  filter(Background != "p6") |>
  filter(Background != "control") |>
  ggplot(aes(
    x = Viral.load,
    y = (total_reads),
    colour = Background
  )) +
  geom_point() +
  geom_smooth(aes(group = Background), se = FALSE) +
  facet_grid( ~ type, labeller = as_labeller(facet_names)) +
  theme_few() +
  theme(
    axis.title.y = element_text(size = 10),
    panel.grid.major = element_line(linewidth=0.1, color = "gray60"),
    panel.grid.minor = element_line(linewidth=0.1, color = "lightgray")
  ) +
  scale_y_log10(labels = scales::trans_format("log10", scales::label_math())) + 
    scale_x_log10(labels = scales::trans_format("log10", scales::label_math())) + xlab("Genome copies") +
  # ggtitle("All") +
  ylab("Total number of reads") +
  scale_color_manual(values = cols2, labels = c("P1", "P2"))

viral_reads <- 
  reads_plot |>
  filter(Background != "p6") |>
  filter(Background != "control") |>
  ggplot(aes(
    x = Viral.load,
    y = (viral_reads),
    colour = Background
  )) +
  geom_point() +
  geom_smooth(aes(group = Background), se = FALSE) +
  facet_grid( ~ type, labeller = as_labeller(facet_names)) +
  theme_few() +
  theme(
    axis.title.y = element_text(size = 10),
    panel.grid.major = element_line(linewidth=0.1, color = "gray60"),
    panel.grid.minor = element_line(linewidth=0.1, color = "lightgray")
  ) +
  scale_y_log10(labels = scales::trans_format("log10", scales::label_math())) + 
    scale_x_log10(labels = scales::trans_format("log10", scales::label_math())) + xlab("Genome copies") +
  # ggtitle("Viral reads") +
  ylab("Number of viral reads") +
  scale_color_manual(values = cols2, labels = c("P1", "P2"))

ATCC_reads <- 
  reads_plot |>
  filter(Background != "p6") |>
  filter(Background != "control") |>
  ggplot(aes(
    x = Viral.load,
    y = (ATCC_reads),
    colour = Background
  )) +
  geom_point() +
  geom_smooth(aes(group = Background), se = FALSE) +
  facet_grid( ~ type, labeller = as_labeller(facet_names)) +
  theme_few() +
  theme(
    axis.title.y = element_text(size = 10),
    panel.grid.major = element_line(linewidth=0.1, color = "gray60"),
    panel.grid.minor = element_line(linewidth=0.1, color = "lightgray")
  ) +
  scale_y_log10(labels = scales::trans_format("log10", scales::label_math())) + 
    scale_x_log10(labels = scales::trans_format("log10", scales::label_math())) + xlab("Genome copies") +
  ggtitle("Spike-in Viral Reads") +
  ylab("Spike-in Viral Reads") +
  scale_color_manual(values = cols2, labels = c("P1", "P2"))

prop_ATCC <- reads_plot |>
  filter(Background != "p6") |>
  filter(Background != "control") |>
  ggplot(aes(x = Viral.load, y = prop_ATCC, colour = Background)) +
  geom_point() +
  geom_smooth(aes(group = Background), se = FALSE) +
  facet_grid( ~ type, labeller = as_labeller(facet_names)) +
  theme_few() +
  theme(
    axis.title.y = element_text(size = 10),
    panel.grid.major = element_line(linewidth=0.1, color = "gray60"),
    panel.grid.minor = element_line(linewidth=0.1, color = "lightgray")
  ) +
    scale_x_log10(labels = scales::trans_format("log10", scales::label_math())) + xlab("Genome copies") +
  ggtitle("Spike-in viral reads") +
  ylab("Proportion") +
  scale_color_manual(values = cols2, labels = c("P1", "P2"))

prop_viral <- reads_plot |>
  filter(Background != "p6") |>
  filter(Background != "control") |>
  ggplot(aes(x = Viral.load, y = prop_viral, colour = Background)) +
  geom_point() +
  geom_smooth(aes(group = Background), se = FALSE) +
  facet_grid( ~ type, labeller = as_labeller(facet_names)) +
  theme_few() +
  theme(
    axis.title.y = element_text(size = 10),
    panel.grid.major = element_line(linewidth=0.1, color = "gray60"),
    panel.grid.minor = element_line(linewidth=0.1, color = "lightgray")
  ) +
 scale_x_log10(labels = scales::trans_format("log10", scales::label_math())) + xlab("Genome copies") +
  # ggtitle("Viral reads") +
  ylab("Proportion of viral reads") +
  scale_color_manual(values = cols2, labels = c("P1", "P2")) + scale_y_continuous(limits=c(0,1.0))
